Uncertainty propagation in neural networks for sparse coding

### 2018-04-12 paper/BayesianLISTA.tex
minor text updates check if they were in paper

@@

\begin{enumerate}
	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
	\item $\mathbf{c} = \mathbf{b} + \mathbf{e}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
\end{enumerate}

@@

\begin{figure}[t]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
\caption{Approximations of Bayesian \textsc{lista}}
%\label{fig:z_new_testing}
\end{figure}

>>>>

\begin{figure}[!t]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
\caption{Approximations of Bayesian \textsc{lista}}
%\label{fig:z_new_testing}
\end{figure}

@@

\begin{enumerate}
	\item $\mathbf{b} = \mathbf{W}\mathbf{y}$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:matrix_const};
	\item $\widehat{\boldsymbol\beta}_{0} = h_\lambda(\mathbf{b})$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
	\item $\mathbf{e}_l = \mathbf{S}\widehat{\boldsymbol\beta}_{l-1}$ is approximated with the Gaussian distribution, which parameters are computed according to lemma \ref{thm:matrix_vector};
	\item $\mathbf{c}_l = \mathbf{b} + \mathbf{e}_l$ is the Gaussian distribution with parameters computed according to lemma \ref{thm:sum_vectors};
	\item $\widehat{\boldsymbol\beta}_{l} = h_\lambda(\mathbf{c}_l)$ is approximated with the spike and slab distribution, which parameters are computed according to lemma \ref{thm:soft_thresholding}.
\end{enumerate}

@@
